Security vs. Maintainability: Fixing Vulnerabilities Obfuscates your Code

### 2019-01-28 paper/ICPC19/icpc19.tex
cleaning
starting results

To validate the maintainability differences in different groups of commits (e.g., baseline and security commits), we use the Paired Wilcoxon signed-rank test \cite{10.2307/3001968} with the significance level $\alpha = 0.05$. In other words, we test the null hypothesis that the maintainability difference between pairs of versions $v_{v-1}$, $v_v$ (i.e., before and after a security-commit) follows a symmetric distribution around $0$. To understand the effect-size, as advocated by the Common-language effect sizes \cite{graw:1992}, we compute the mean difference, the median of the difference, and the percentage of cases that reduce maintainability.

@@

>>>>

To validate the maintainability differences in different groups of commits (e.g., baseline and security commits), we use the Paired Wilcoxon signed-rank test \cite{10.2307/3001968} with the significance level $\alpha = 0.05$. In other words, we test the null hypothesis that the maintainability difference between pairs of versions $v_{v-1}$, $v_v$ (i.e., before and after a security-commit) follows a symmetric distribution around $0$. However, when the difference between groups is zero, the observations are discarded. Thus, we use a more robust approach of the wilcoxon test, the Wilcoxon test by Pratt which provides an alternative that incorporates the cases where the maintainability difference is zero \cite{10.2307/2282543}. To understand the effect-size, as advocated by the Common-language effect sizes \cite{graw:1992}, we compute the mean difference, the median of the difference, and the percentage of cases that reduce maintainability.

@@

In total, this study evaluates $607$ security and baseline commits from 94 different open-source projects distributed among 5 different main types of software, Figure \ref{fig:domain}. The following section presents the results obtained for each research question.
